\begin{solution}[label=ques:1a]
  \begin{question}
    Suppose Alice is able to send 1 qubit to Bob, and nothing else.
Describe a protocol that lets Bob learn the bit of his choice with
probability $\cos^2(\pi/8) \approx 85\%$. You may assume Alice and Bob can perform any quantum gate/apply any unitary to qubits in their possession that you want.
Give an analysis or proof that it achieves this success probability.
\\ \textit{Hint: You might find the following states useful:}
\begin{gather*}
\cos(\pi/8)\ket{0}+\sin(\pi/8)\ket{1},\quad \sin(\pi/8)\ket{0}+\cos(\pi/8)\ket{1}\\
\cos(\pi/8)\ket{0}-\sin(\pi/8)\ket{1},\quad \sin(\pi/8)\ket{0}-\cos(\pi/8)\ket{1}
\end{gather*}
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    A protocol that lets Bob learn the bit of his choice with probability $\cos^2(\pi/8)$ is
    \protocol{Protocol for Kinda-dense coding}{Protocol used by Alice and Bob}{proto:densealicebob}{
      \begin{enumerate}
        \item \textbf{Alice:}
          \begin{enumerate}
            \item Prepare her qubit in the state $Z^yX^xR_y(\pi/8)\ket{0}$.
            \item Send the qubit to Bob.
          \end{enumerate}
        \item \textbf{Bob:}
          \begin{enumerate}
            \item If Bob wants to learn $x$, measure the qubit in the standard basis and return the output.
            \item If Bob wants to learn $y$, measure the qubit in the Hadamard basis and return the output.
          \end{enumerate}
      \end{enumerate}
    }

    The success probability of Bob learning either bit for every possibility of $x, y$ is $\cos^2(\pi/8)$ and therefore, the overall success probability is $\cos^2(\pi/8)$. It is easy to see why this is the case. We enumerate the state Alice sends to Bob for every possibility of $x, y$:
    \begin{enumerate}
      \item $x = 0, y = 0$: Alice sends $R_y(\pi/8)\ket{0} = \cos\pi/8\ket{0} + \sin\pi/8\ket{1}$. If Bob measures in the standard basis, he will get $0$ with probability $\cos^2(\pi/8)$. If Bob measures in the Hadamard basis, he will get $0$ with probability $\cos^2(\pi/8)$.
      \item $x = 1, y = 0$: Alice sends $XR_y(\pi/8)\ket{0} = \sin\pi/8\ket{0} + \cos\pi/8\ket{1}$. If Bob measures in the standard basis, he will get $1$ with probability $\cos^2(\pi/8)$. If Bob measures in the Hadamard basis, he will get $0$ with probability $\cos^2(\pi/8)$.
      \item $x = 0, y = 1$: Alice sends $ZR_y(\pi/8)\ket{0} = \cos\pi/8\ket{0} - \sin\pi/8\ket{1}$. If Bob measures in the standard basis, he will get $0$ with probability $\cos^2(\pi/8)$. If Bob measures in the Hadamard basis, he will get $1$ with probability $\cos^2(\pi/8)$.
      \item $x = 1, y = 1$: Alice sends $ZXR_y(\pi/8)\ket{0} = \sin\pi/8\ket{0} - \cos\pi/8\ket{1}$. If Bob measures in the standard basis, he will get $1$ with probability $\cos^2(\pi/8)$. If Bob measures in the Hadamard basis, he will get $1$ with probability $\cos^2(\pi/8)$.
    \end{enumerate}
    Hence, proved.
  \end{proof}
\end{solution}

\begin{solution}[label=ques:1b]
  \begin{question}
    Now suppose Alice can no longer send a qubit and she is limited to 1 bit of classical communication only. And
    suppose that now the bits $x$ and $y$ are uniformly random and independent of each other.  
    Describe a protocol where Alice sends one classical bit to Bob and Bob learns the bit of his choice with $75\%$ chance of success.
    \\ In other words, describe a protocol where Alice sends a classical bit to Bob, then Bob decides whether he would like to learn $x$ or $y$ (Bob's choice is his own: you cannot assume it's uniformly random), he performs some series of steps which results in some designated output bit, and there is a $75\%$ chance that this bit matches the value of the bit he wanted.
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    In the classical case, Alice simply sends $x\times y$ and Bob decodes the input bit as the bit he wants to learn. This protocol succeeds with $75\%$ probability irrespective of Bob's choice because the inputs $x$ and $y$ are uniformly distributed. Without loss of generality, assume Bob wants to learn $x$. The probability of Bob learning $x$ is $1$ if $x = 0$ and $0.5$ if $x = 1$ (since $y$ will be $1$ only half the time). Therefore, the net probability of Bob learning $x$ is $0.75$. The same argument holds for the case when Bob wants to learn $y$.
  \end{proof}
\end{solution}
