\begin{solution}[label=ques:1a]
  \begin{question}
    Suppose the top measurement is in the $\ket{+}/\ket{-}$ basis.
What is the probability we observe $\ket{+}$ on the top qubit?
Show your work.
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    Measuring in the $\ket{+}/\ket{-}$ basis is the same as applying a $H$ gate and then measuring in the $\ket{0}/\ket{1}$ basis. Therefore, the equivalent state before measurement in the $\ket{0}/\ket{1}$ basis is,
    \begin{equation}
      \begin{split}
        \ket{\psi} &= \frac{(\ket{0} + \ket{1})\ket{0} + \sqrt{2}(\ket{0} - \ket{1})\ket{0} + \sqrt{2}(\ket{0} + \ket{1})\ket{1} - (\ket{0} - \ket{1})\ket{1}}{\sqrt{12}}\\
        &= \frac{\ket{0}\left((\sqrt{2} + 1)\ket{0} + (\sqrt{2} - 1)\ket{1}\right) - \ket{1}\left((\sqrt{2} - 1)\ket{0} - (\sqrt{2} + 1)\ket{1}\right)}{\sqrt{12}}
      \end{split}
    \end{equation}
    Since the amplitudes of the the $\ket{0}$ and $\ket{1}$ states are equal, the probability of observing $\ket{+}$ on the top qubit is $50\%$.
  \end{proof}
\end{solution}

\begin{solution}[label=ques:1b]
  \begin{question}
    If we observe $\ket{+}$ on the top qubit, then what is the state of the bottom qubit? Show your work.
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    The state of the bottom qubit will be the normalised state that is tensored with the $\ket{0}$ in the state obtained in Question~\ref{ques:1a}. Therefore, the state of the bottom qubit is $\frac{\left(\sqrt{2} + 1\right)\ket{0} + \left(\sqrt{2} - 1\right)\ket{1}}{\sqrt{6}}$.
  \end{proof}
\end{solution}

\begin{solution}[label=ques:1c]
  \begin{question}
    What is the probability the joint outcome of the two measurements is $\ket{+-}$?
    Show your work.
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    Since we know the probability of obtaining $\ket{+}$ state on the first qubit is $50\%$, it is enough to compute the probability of obtaining a $\ket{-}$ state on the residual state obtained in Question~\ref{ques:1b} and multiply it by $1/2$. To obtain the probability of obtaining a $\ket{-}$ state, we again apply a $H$ gate and measure in the $\ket{0}/\ket{1}$ basis. The equivalent state is,
    \begin{equation}
      \begin{split}
        \ket{\psi'} &= \frac{\left(\sqrt{2} + 1\right)(\ket{0} + \ket{1}) + \left(\sqrt{2} - 1\right)(\ket{0} - \ket{1})}{\sqrt{12}}\\
        &= \sqrt{\frac{2}{3}}\ket{0} + \sqrt{\frac{1}{3}}\ket{1}
      \end{split}
    \end{equation}
    Therefore, the probability of obtaining a $\ket{-}$ on the second qubit is $1/3$ and therefore, the resultant probability of getting $\ket{+-}$ is $1/6$.
  \end{proof}
\end{solution}
