\begin{solution}[label=ques:2a]
  \begin{question}
    What is the minimum number of people who need to call in before the probability of a match being found is at least 50\%?
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    \textit{Note: For all parts, this question is interpreted as trying to find the probability that we get a match with $p$ probability (where $p = 50\%$ or $99\%$ depending on which part the answer is for) at or before the $n^\textsuperscript{th}$ person calls. This probability is different from the probability that the station succeeds at exactly the $n^\textsuperscript{th}$ call and fails for all $i < n$.}

    We compute the probability that no match happens until the $n^\textsuperscript{th}$ person calls. This will be $1$ minus the probability that we want. The probability can be computed as:
    \begin{equation}
      \begin{split}
        &\prob{\text{no match}} = \frac{\binom{365}{n}\cdot n!}{365^n}\\
        \implies &\prob{\text{match}} = 1 - \frac{\binom{365}{n}\cdot n!}{365^n}
      \end{split}
      \label{eq:bbnomatch}
    \end{equation}
    Therefore, the probability of a match is at least 50\% when $n = 23$ (on plugging in Python).
  \end{proof}
\end{solution}

\begin{solution}[label=ques:2b]
  \begin{question}
    How about the minimum number of people needed before there is a 99\% chance of the contest coming to a close?
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    On plugging in the numbers in Python again, the probability of a match is at least 99\% when $n = 57$.
  \end{proof}
\end{solution}

\begin{solution}[label=ques:2c]
  \begin{question}
    Imagine after running the contest for a few days the station decides they aren't being generous enough and so change the rules as follows: Instead of the contest ending as soon as there's a match found between any two contestants on the list it now ends when a match is found between specifically the first caller of the day and any other contestant. 

Under these new rules what is the minimum number of people needed before there is a 50\% chance of the contest closing? How about for a 99\% chance?
  \end{question}
  \tcblower{}
  \begin{proof}[Solution]
    Again, similar to Question~\ref{ques:2a}, we can compute the probability of no match happening until the $n^\textsuperscript{th}$ person calls. This will be $1$ minus the probability that we want. The probability can be computed as:
    \begin{equation}
      \begin{split}
        &\prob{\text{no match}} = \left(\frac{364}{365}\right)^{n-1}\\
        \implies &\prob{\text{match}} = 1 - \left(\frac{364}{365}\right)^{n-1}
      \end{split}
      \label{eq:mbbnomatch}
    \end{equation}
    Therefore, the probability of a match is at least $50\%$ when $n = 254$ and it is at least $99\%$ when $n = 1680$ (on plugging in Python).
  \end{proof}
\end{solution}
